---
title: "Gov 50 Final Project"
author: "Sebastian Lennox"
description: "Climate Change Project"
output:
  distill::distill_article:
    self_contained: false
---



## Project thoughts

(Very rough draft, to be improved) 
I hypothesize that the least intense periods of Carbon Dioxide increase in the atmosphere occured during the 1990s and 2000s. This is because the detrimental effects of Carbon Dioxide in the atmosphere had been researched and observed, and certain global movements, including the Kyoto Protocol of 1997, had been signed with the hopes of reducing emissions from entire countries. In this project, I will be observing the trends of Carbon Dioxide content in the atmosphere and attempt to use this information to infer why certain spikes and drops occured based on other carbon emission data brought in. The variable is measured in PPM (parts per million) of CO2 in the atmosphere. The explanatory variable at the moment is years, but will eventually transition to carbon emissions in specific countries (also likely measured in PPM). If the data demonstrates low carbon emissions in all countries during the 1990s and 2000s, it is likely that the PPM of CO2 will also reflect this. However, if there is even a slight discrepancy in CO2 production during these decades, my hypothesis will likely be disproved. 

```{r echo = FALSE}
library(tidyverse)
library(readr)

CO2_Content <- read.csv("~/Downloads/co2-mm-mlo_csv.csv")

head(knitr::kable(CO2_Content), 10)

CO2vsYears <- ggplot(CO2_Content, aes(x = Interpolated)) + 
  geom_histogram() + 
  labs(x = "Interpolated CO2 Content (in PPM)", 
       y = "Frequency of CO2 Contents",
       title = "Frequency of CO2 Content in months from 1958 to 2018", 
       caption = "Interpolated data based on Average and Trend data") 
CO2vsYears


```

```{r echo = FALSE}
CO2vsConsistency <- ggplot(CO2_Content, aes(x = Number.of.Days, y = Interpolated)) + 
  geom_point() + 
  labs(x = "Number of Daily Averages Measured for a Month", 
       y = "Interpolated CO2 Content (in PPM)",
       title = "CO2 Content in the Atmosphere as a Function of the Number of Days an Average CO2 Content was Measured for a Particular Month", 
       caption = "Interpolated data based on Average and Trend data") +
  geom_smooth(method = "lm", se = FALSE, color = "blue", linewidth = 1.5)
CO2vsConsistency
```
The above data does not support my hypothesis. In the graph, the line of best fit indicates that with the more daily averages collected (-1 and 31 being the extremes for the number of averages collected in a month), there was more CO2 content in the atmosphere. This disagrees with my hypothesis because the months with no daily average measurements (as signified by -1) were concentrated in the early years of this data collection (pre-1974), whereas later years (1990s-2000s) featured several months with significant daily averages recorded. Ultimately, this seems to indicate that the 1990s and 2000s had high amounts of CO2 concentration in the atmosphere. However, this analysis also does not take into account the years between 1973 and 1990 in addition to those between 2010 and 2018 that had high numbers of data collection across a month. Grouping the data more specifically within these ranges in another analysis may provide a different result with respect to my hypothesis. 
